\chapter[Radio Halos]{Radio Halos}
\label{Chap:Background}
\section{Synchrotron emission}
Since the first discoveries of diffuse radio emission, much research has been devoted towards understanding the mechanisms behind the production of synchrotron electrons. These electrons are also known as `cosmic ray' electrons (CRe) or non-thermal electrons to differentiate them from the thermal electrons of the ICM. The CRe have an individual energy $E=\gamma m_e c^2$ dependent on their Lorentz factor $\gamma$. 
\begin{equation}
    \gamma = \left(1-\frac{v^2}{c^2}\right)^{-\frac12}
\end{equation}
In the case of radio halos we can expect $\gamma\gtrsim10^4$ which corresponds to velocities within $10^{-4}\%$ of the speed of light. Throughout their radiative lifetime CRe produce radio synchrotron emission with energy as a function of the perpendicular magnetic field and their Lorentz factor. This is broadly a continuum radiation with the synchrotron power described by the following equation \citep{Feretti2008}. 
\begin{equation}
    -\frac{dE}{dt} = \frac{2e^4}{3m_e^4c^7}(B \sin\theta)^2E^2
\end{equation}
They also interact with thermal protons within the ICM in a process called inverse Compton (IC) scattering.\footnote{Standard Compton scattering has ultrarelativistic photons interacting with thermal electrons, the opposite to what we are considering.} The scattered photon has a boosted energy that is proportional to its orginal energy. In units of frequency this relation is:
\begin{equation}
    \nu_p = \frac34\gamma^2 \nu_{p,0}
\end{equation}
For CRe under consideration this results in a factor $\sim10^6$. The CMB is a source of thermal photons throughout the cluster with a temperature of $\text{T} = 2.73 \text{K}$, to which the Planck function peaks at $\nu \approx 1.6\times10^{11}$ Hz. Which results in high energy X-ray emission \citep{Sarazin1999, Govoni2004}. 

Synchrotron radiation is insufficient to directly measure the magnetic field, and the standard method is to instead measure the equipartition field $B_{eq}$. This field is found by minimising the total energy of the magnetic field potential and that of the relativistic particles. The IC emission is independent of the magnetic field however, meaning that comparisons between these values would allow direct measurement of the magnetic field strength \citep{Govoni2004, Wik2014}. Unfortunately, detection of the X-ray IC component is difficult due to low X-ray energies dominanted by the thermal component, while upper energies have lacking spatial resolution in current instruments. An interesting topic in its own right, IC emission and cluster magnetic fields are outside the scope of this thesis.

\section{Lifetime of synchrotron emission}

The energy losses of the CRe as they interact with the electromagnetic fields and particles in the ICM eventually result in them no longer being energetic enough to produce radio emission. Considering losses due to synchrotron and IC processes, the lifetime of a CRe can be given as the following function of the magnetic field in the ICM $B$ and the magnetic field of the CMB $B_{CMB}$. 

\begin{equation}
    \tau = 32 \frac{B^{\frac12}}{B^2 + B^2_{CMB}}\left[(1+z)\nu\right]^{-\frac12}
\end{equation}

We can also define $B_{CMB} = 3.25(1+z)^2$ $\mu$G to account for the redshift of the clusters in question. As observed minihalos have redshifts in the range $[0.1, 0.3]$ and magnetic fields within the ICM are estimated at $\lesssim$ $\mu$G, the maximum expected lifetime of a CRe is about $10^{8}$ years \citep{Sarazin1999, Ferreti2012, Gitti2018}. 

Then we can find the expected extent for these particles, in absentia of external forces, as $\sim 10^{16}$ m or $1$ pc. This is orders of magnitude below the extents of observed diffuse radio emission, so we then consider that the CRe are moving within the bulk motion and magnetic fields of the ICM. If we assume that there is a strong of turbulence to promote diffusion of CRe, we can use the Bohm approximation $D = \frac{k_B T}{eB}$, which models the diffusion of plasma across a magnetic field. \citet{Bagchi2002} finds that The expected length-scale of this diffusion (at $z=0.3$) is that of a random walk across its lifetime with a diffusion coefficient $\kappa$ and length-scale $L_{diff}$,\footnote{The length-scale diffusion is calculated as a random walk, scaling with the square root of time, rather than linearly.}
\begin{equation}
    \kappa = 3.31\times10^{21} \left(\frac E{\text{GeV}}\right)\left(\frac B{10^{-7}}\right) \>\text{m s}^{-1}
\end{equation}
\begin{equation}
    L_{diff} = \sqrt{\kappa\tau} = 6.7\left(\frac B{10^{-7}}\right)^{-\frac12}\>\text{pc}
\end{equation}

Once again, we find that the expected diffusion and halo produced by a point source is measured in the 10s of parsecs, far below the kiloparsec and megaparsec halos observed. Therefore, we must assume that these particles are being re-accelerated or produced \textit{in-situ} by a process that is extended over the kiloparsec scale and long-lived across the particle lifetime. 

In the case of CRe within the thin plasma of the ICM, we make the standard assumption that the population of CRe is homogeneous, isotropic, and follows a power-law energy distribution $n(E) \propto E^{-\delta}$. From this we then predict the following basic observables (see \citet{vanWeeren2019}, \citet{Ferreti2012} and references within). \stickynote{Add graph of spectral shapes?}

\begin{enumerate}
    \item The synchrotron emissivity is dependent on the number density of the CR electrons and the strength of the magnetic field. As such, the emissivity also follows a power-law $S(\nu) \propto \nu^{-\alpha}$ which is related to $\delta$ by $\alpha = (\delta - 1)/2$. Typical minihalo spectral indices are steep with $\alpha > 1$.
    \item Over time the emitting particles lose energy, which changes the particle energy distribution and therefore, the emitted radio spectrum. This appears as a steepening or curved spectrum, rather than a flat power-law. The break frequency at which this occurs is related to the time of acceleration. This means that radio events that have stopped will show an aged spectrum with a characteristic break, such as radio relics, while ongoing events are continually injecting new particles and don't feature the same steepening due to age. 
    \item Radiation from CR electrons passing through a uniform magnetic field is linearly polarised. Non-uniform and disordered fields reduce the linear polarisation. 
\end{enumerate} 

 

A

\section{Production mechanisms}

The 

\subsection{Turbulent re-acceleration}

\label{sec:BG_reacceleration}
\begin{itemize}
    \item What is the process here.
    \item How manifest spectrally.
    \item How manifest spatially.
\end{itemize}

\subsection{Hadronic Production}
\label{sec:BG_hadronic}
\begin{itemize}
    \item What is the process for hadronic production
    \item How does this manifest spectrally and evolve. What should we expect observationally here based on simulation work.
    \item How does this manifest spatially and evolve, what should we see observationally.
\end{itemize}



\subsection{Large Radio Halos}
\begin{itemize}
    \item Use similar physics but much larger scale. 
    \item Some basics things about previous research in differentiating production. 
    \item Gamma ray non-detection.
    \item General consensus is that its re-acceleration.
\end{itemize}

\subsection{Minihalos}
\begin{itemize}
    \item These are much smaller, so therefore much harder to observe. Difference to large radio halos.
    \item Similarities between host clusters (CC), general properties of spectral index etc.
\end{itemize}









\subsection{Previous minihalo studies}
\begin{itemize}
    \item Generally look at lower frequencies, or a singular study for a particular minihalo.
    \item Want to look at more minihalos in a more holistic manner. 
    \item Some findings from previous papers e.g. RXJ1720, MS1455+2232 in basic detail. (more detail on the per-halo discussion).
\end{itemize}
