\chapter[Discussion]{Discussion}
\label{Chap:Discussion}

This sample of 12 clusters hosting minihalos was observed at 10 GHz to investigate the possibility of high-frequency spectral steepening. Of these, a robust measurement of the total minihalo flux density was obtained for four clusters. Combining these measurements with the results of previous studies, 75\% of clusters exhibit a well-fitted single power-law spectrum. For a single cluster, A478, tentative evidence for steepening is observed. These results are summarised in the following section.

\section{Summary of results}

\subsection{Clusters consistent with single power-law}
The minihalo observed within RXJ1720+2638 is one of the most well-examined examples, though previous studies have stated conflicting interpretations. Notably, an 8.44 GHz measurement suggested tentative evidence for steepening relative to lower frequencies \citep{Giacintucci2014a}, while \textit{uv}-plane modelling at 15.5 GHz was consistent with a single power-law spectrum \citep{Perrott2021}. The results of this thesis provide direct observational evidence in support of a single power-law spectrum up to at least 10 GHz. This is consistent with the conclusions of \citet{Perrott2021}, who argued that incomplete \textit{uv}-coverage at 8.44 GHz artificially reduced the measured flux density. 

The flux density measured over the tail region of the RXJ1720+2638 minihalo is approximately three times higher than that predicted by extrapolation of previous measurements. The calculated spectral index reflects this, being flatter than previously reported. \citet{Giacintucci2014a} reported that spatial steepening was exhibited along the tail. As such, the averaged spectral index over the tail may differ at 10 GHz to the lower frequency studies. The detectable high-frequency emission is found to extend over only approximately half of the masked tail region. This reduction in spatial extent with increasing frequency is consistent with a steepening spectral index along the tail.

The findings for RXCJ1115+0129 are somewhat less constraining, primarily due to the limited number of flux density measurements for this minihalo. The previous study by \citet{Trehaeven2023} found a spectral index of $\alpha=1.0\pm1.1$ between 1--1.5 GHz, with the uncertainty dominated by subtraction errors. The results of this thesis are consistent with their mean value and reduce the uncertainty by approximately a factor of six. Flux density uncertainty still remains dominated by source subtraction. The northern and southern spatial steepening reported in the previous study was not explored in depth for this thesis. However, the narrower observed spatial extent at 10 GHz is nearly aligned with the direction of their measured steepening. A spatially resolved point-to-point analysis combining the 1.3 GHz MeerKAT data with the 10 GHz observations presented here would provide a more robust test of this feature.

Several previous flux density measurements for the RXJ2129+0005 minihalo were available for comparison with the value measured for this thesis. The 10 GHz flux density is slightly higher than expected from the extrapolation of the previous studies, although the $1\sigma$ uncertainties overlap. The excess flux may arise from two regions of emission near the masking boundary, including the unsubtracted source S2 and a diffuse region to the east (see Figure \ref{fig:rxj2129_sub_image}). These may contaminate the masked area and introduce flux not associated with the minihalo. The complex masking region defined by \citet{Giacintucci2014} was approximated here by an ellipse, which further modifies the measured flux density. Notably, the flux density measured within the $3\sigma$ contour is less than half that of the larger mask ($S_{3\sigma} = 0.15\pm0.1$ mJy compared to $S_{mask} = 0.41\pm0.1$ mJy), which demonstrates the sensitivity of the integrated flux to the adopted mask.

\subsection{Potential curvature for A478}

The final cluster measured for this thesis, A478, presents a more intriguing case. Previous studies placed only an upper limit on the spectral index of $\alpha<1$, whereas the flux density measured here shows a far greater spectral index of $\alpha = 2.02\pm0.10$. The in-band spectral index is even steeper at $\alpha = 3.34\pm0.18$, suggesting significant spectral curvature between 1.4 and 10 GHz. This result should be interpreted with caution, however, as it is based upon only two direct measurements and one non-detection. The adopted mask and \textit{uv}-range likely differ from those used by \citet{Giacintucci2014} and \citet{Savini2019}. Spatial filtering at 10 GHz may result in missing flux, analagous to the 8.44 GHz measurement of RXJ1720+2638. Additional intermediate-frequency observations (e.g. 144 MHz to 5 GHz) are required to determine whether this apparent steepening reflects genuine particle ageing or residual systematic effects. Nevertheless, A478 remains an outlier compared to the other clusters in this sample.

\subsection{Spectral implications for production mechanisms}

For the turbulent reacceleration scenario, the radio spectrum is expected to steepen towards high frequencies. This is caused by the balancing of reacceleration efficiency and the CRe energy losses from synchrotron and inverse Compton radiation. Through simulation, \citet{ZuHone2013} predict that steepening from a single power-law occurs approximately beyond 1 GHz (see Figure \ref{fig:spectral_comparison}). Their simulated minihalo also found exhibited spectral indices in the range $\alpha\approx1.5$--2. These results considered only a single initial injection of CRe. This is not entirely accurate if the minihalo has an embedded AGN, as is the case for many clusters in this sample (e.g RXJ1720+2638, A1413, 2A0335+096, etc). The jets and lobes of AGN are a source of CRe injected into the core of the cluster. Depending on the CRe and energy injected, this may counteract steepening entirely.

In comparison, the hadronic scenario continually refreshes the CRe population. \citet{ZuHone2015} found that this resulted in a single power-law spectrum to high frequencies, with a spectral index dependent on the energy spectrum of the CRe. Minor turbulence within the region had a negligible effect on the integrated spectrum, with the found spectral index as $\alpha\approx1.1$. 

The clusters RXJ1720+2638, RXCJ1115+0129, and RXJ2129+0005 exhibit total 10 GHz flux densities consistent, within uncertainties, with the extrapolated single power-law spectra derived from lower-frequency measurements. Their associated spectral indices are in the range $\alpha\approx1$--$1.1$. These findings are more naturally explained by the hadronic scenario, than by the reacceleration mechanism for the production of the minihalo emission. In contrast, the minihalo within the cluster A478 appears more consistent with the reacceleration mechanism. 

Given this evidence, the findings suggest that both mechanisms may contribute to the overall minihalo emission and are dependent on the local cluster environment. This is reinforced by the presence of steepening along the tail of RXJ1720+2638. Evidence indicates the outer region is where turbulent acceleration begins to dominate the emission spectrum, outside of a hadronically dominated core. Both mechanisms being active within the minihalo at different scales is consistent with the discussions of previous studies (e.g. \citealp{Perrott2021,Riseley2024}). 

Alternatively, turbulent acceleration could be the dominant mechanism in all clusters, with ongoing AGN activity offsetting the intrinsic spectral steepening. Under this interpretation, A478 would represent a cluster where the AGN-driven injections is comparatively weak or absent. 

AGN activity can be approximated using the rest-frame 1.4 GHz radio luminosity of the BCG, $L_{1.4\>\mathrm{GHz}}$. This can be calculated from the redshift $z$,\footnote{The cluster redshift is adopted as a proxy for the BCG redshift, which is sufficient for this comparative estimate.} the luminosity distance of the AGN $D_L$ (which is based on the redshift and cosmology), the spectral index $\alpha$, and measured flux density $S_\nu$ at the observing frequency $\nu$ via,
\begin{equation}
    L_{\nu_{\mathrm{rest}}} = \frac{4\pi D_L^2}{(1+z)^{1-\alpha}}\left(\frac{\nu_{\mathrm{rest}}}{\nu}\right)^{-\alpha}S_\nu
\end{equation}
The derived luminosity powers for the four clusters with minihalo flux measurements are presented in Table \ref{tab:agn_power}. The BCG of A478 exhibits radio power comparable to that of RXJ1720+2638, which hosts sub-parsec jets \citep{Perrott2023}. This suggests that the activity of this BCG is unlikely to be significantly less than systems where this steepening is not observed. Consequently, the lack of strong AGN activity cannot easily explain the apparent spectral steepening in A478. Further work in optical identifiers or high-resolution radio imaging would be required to investigate the level of AGN activity more definitively.

\begin{table}[h]
    \centering
    \begin{threeparttable}

        \begin{tabular}{lccc}
            \toprule
            Cluster & L$_{1.4\,\mathrm{GHz}}$ (this thesis) & L$_{1.4\,\mathrm{GHz}}$ (Lit.) & Reference \\
             & ($\times10^{24}$ W Hz$^{-1}$) & ($\times10^{24}$ W Hz$^{-1}$) & \\
            \midrule
            RXJ1720+2638  & $0.47 \pm 0.18$ & $0.50\pm0.02$ & \citet{Giacintucci2014a} \\
            A478          & $0.58 \pm 0.21$ & $0.60\pm0.03$ & \citet{Giacintucci2014} \\
            RXCJ1115+0129 & $3.0 \pm 1.8$ & $3.2\pm0.4$ & \citet{Trehaeven2023} \\
            RXJ2129+0005  & $3.9 \pm 1.2$ & $3.1\pm0.2$ & \citet{Kale2015} \\
            \bottomrule
        \end{tabular}
        
        \caption{Radio luminosity for the BCG at 1.4 GHz. Estimates from this thesis are presented in comparison to literature value derived at from lower-frequency measurements.}
        \label{tab:agn_power}
    \end{threeparttable}
\end{table}

\section{Measurement Limitations}
There are several fundamental observational limitations affecting the detectability of minihalos in this study. The primary constraints arise from the maximum recoverable scale, surface brightness sensitivity, and angular resolution of the interferometer configuration. Effects arising from these limitations are discussed here.

\subsection{Maximum recoverable scale}
The largest angular scale that the interferometer can recover is set by the minimum projected baseline length. For these VLA observations, the shortest baselines correspond to 1 k$\lambda$. Approximating the angular scale as $\theta \approx 1/\vec u$ yields $10^{-3}$ rad or $\sim\!3.44$ arcminutes. 

For a characteristic minihalo diameter of $\sim\!300$ kpc, this angular scale corresponds to a minihalo located at redshift $z \sim 0.07$. Below this redshift, emission at scales comparable to or larger than this minihalo diameter may be partially resolved out, leading to an underestimation of the total flux density. 

This effect is most relevant for three clusters in this sample, 2A0335+096, A2626, and A1795. Of these clusters, only 2A0335+096 has a source-subtracted image. For this cluster $3.44'$ corresponds to $\approx150$ kpc. Diffuse emission extending beyond this scale will not be fully recovered. The lowest-redshift cluster for which a total 10 GHz flux density was successfully measured is RXJ1720+2638 at $z=0.160$. This corresponds to a maximum physical scale of $\sim\!570$ kpc, suggesting that spatial filtering is unlikely to significantly bias the integrated flux densities reported here. 

Similarly, studies that have significantly different \textit{uv}-coverage can be biased by the different fluxes they are able to recover. Matching the \textit{uv}-coverage with prior studies, as performed for RXJ1720+2638, further ensures any spatial filtering is consistent between studies.

\subsection{Surface brightness sensitivity}

The surface brightness sensitivity is limited by image noise, which arises from residual RFI, calibration uncertainties, and instrumental thermal noise. For the 10 GHz observations presented here, the typical rms noise level is approximately $3$ $\mu$Jy beam$^{-1}$. 

For steep-spectrum or intrinsically low-brightness minihalos, emission may fall below the adopted $3\sigma$ detection threshold. This can artificially reduce the apparent spatial extent of the emission relative to lower-frequency observations, where surface brightness is higher. In such cases, only lower limits on the spectral index can be derived. This would be relevant for a spatial analysis of the spectral index within the tail of the RXJ1720+2638 minihalo, where only half the region is greater than the detection threshold. As discussed previously, spatial masks defined in earlier studies were adopted where available to ensure consistency in flux density measurements. 

The choice of adopted mask is of particular importance for A478, where the spatial extent of the minihalo observed at 10 GHz (approximately 80 kpc by 40 kpc) is far smaller than that of previous studies (approximately 150 kpc by 120 kpc \citep{Giacintucci2014}). As no mask was available, the final integrated area is likely far smaller, resulting in a systematic underestimation. Conversely, several compact sources are detected in this thesis that are not noted during the subtraction process at lower frequencies. This may instead bias those flux densities higher, resulting in a steeper observed spectrum.

\subsection{Angular resolution}
The angular resolution, defined by the restoring beam, has the greatest impact on the accuracy of the source subtraction. For the 10 GHz observations, the typical restoring beam is approximately $4"\times3"$. Higher angular resolution improves the modelling of compact sources and their associated lobes or jets, enabling more effective separation from the diffuse minihalo emission.

Many compact sources are unresolved at this beam size. Improved resolution allows subtraction to occur over smaller areas, thereby reducing subtraction uncertainties. Since the subtraction error scales with the area over which the model is removed, $\sigma_{sub} \propto A_{sub}$, improved resolution directly reduces residual contamination. As discussed previously, the inclusion of C-configuration data provides the necessary angular resolution with regards to the joint imaging process.

\section{Incomplete clusters}
For the majority of the remaining clusters in this sample a minihalo is detected at 10 GHz. However, difficulties encountered during the subtraction of contaminating emission prevented robust estimation of the minihalo flux in several cases. These difficulties can be categorised as arising from (i) variability of compact sources between observing epochs and (ii) residual diffuse emission not associated with the minihalo in the subtracted image. 

Variability of compact sources between observations at different epochs presents a significant challenge for self-calibration and source subtraction. Point source modelling was performed independently for each dataset in order to mitigate this effect. However, this did not fully resolve the residual artefacts in the individual models nor the joint image. The C-configuration observations were typically the dominant contributor to subtraction errors in the combined datasets image, although the precise reason behind this remains unclear. Possible factors are the \texttt{tclean} parameters for imaging of the point sources and residual calibration errors.

The clusters where a minihalo was not detected at 10 GHz are A1795 and A2626. In both cases, the absence of a clear detection is attributed to imaging artefacts obscuring potential diffuse emission, rather than insufficient surface brightness sensitivity. These clusters contain bright central AGNs that complicate the self-calibration process. It is plausible that with additional refinement of the self-calibration process, a reliable image of the minihalo emission could be recovered. 

The models used for source subtraction were constructed using a fixed \textit{uv}-cut and imaging parameters derived from an analysis of a single cluster, RXJ1720+2638 (see Section \ref{sec:source_subtraction}). Although manual inspection of each resulting image was performed, these parameters likely require optimisation on a per-cluster basis. A key systematic limitation arises because the adopted \textit{uv}-cut corresponds to a constant angular scale on the sky, rather than a constant physical scale.

The clusters in this sample span physical scales between 0.72 and 7.5 kpc arcsec$^{-1}$, increasing with redshift under the adopted cosmology. Consequently, the same angular \textit{uv}-cut corresponds to substantially different physical scales across the sample. RXJ1720+2638 lies at an intermediate redshift within the cluster sample. For lower-redshift clusters an identical \textit{uv}-cut selects smaller physical scales. In such cases, diffuse emission from AGN lobes may not be fully included in the subtraction model, leading to residual contamination in the subtracted image (e.g. 2A0335+096). 

Conversely, for higher-redshift clusters, the same \textit{uv}-cut corresponds to larger physical scales. This increases the risk that extended minihalo emission is partially incorporated into the subtraction model, resulting in overestimation of compact source flux densities, and subsequently, over-subtraction in the final image (e.g ACTJ0022-0036). The impact of adopting a constant angular \textit{uv}-cut is therefore dependent on the minihalo extent, cluster redshift, and the morphology of embedded radio sources.

\section{SZ effect}
The SZ effect represents a potential contaminant to the flux densities measured in this thesis. As it arises from IC-scattering throughout the cluster, it is naturally a cluster-scale phenomenon extending well beyond the spatial extent of the minihalo. Such a large-scale structure may be partially sampled at the shortest baselines of the 10 GHz observations. At 10 GHz this manifests as a negative signal, causing an underestimation of the minihalo flux. However, the relatively low frequency of these observations compared to the thermal SZ spectrum, means that the expected amplitude of this decrement is small.

\citet{Perrott2021} estimated the maximum SZ signal for RXJ1720+2638 for the VLA observation at 8.44 GHz. They found a negative maximum amplitude of approximately 80 $\mu$Jy at the shortest baselines. Given the similar observing frequency and comparable interferometer configuration, this provides a reasonable estimate for the expected SZ signal. For RXJ1720+2638 this is negligible compared to the measured minihalo flux and lies well within the quoted uncertainty ($\sigma=0.56$ mJy).

The remaining clusters where minihalo fluxes are obtained (A478, RXCJ1115+0129, and RXJ2129+0005) have masses within $-26\%$ to $+18\%$ of RXJ1720+2638. As the SZ effect scales primarily with the integrated thermal pressure (and therefore cluster mass), a very conservative upper bound of $<0.1$ mJy is considered for all clusters. This is close to or within the measurement uncertainties for RXCJ1115+0129 ($\sigma=0.10$ mJy) and RXJ2129+0005 ($\sigma=0.15$ mJy). For A478, this represents approximately 33\% of the measured flux and over double the stated uncertainty ($\sigma=0.03$ mJy). However, this difference is insufficient to reconcile the order of magnitude discrepancy to the lower limit on the spectral index reported by \citet{Savini2019}.

Given that the SZ contribution is comparable to or below the measurement uncertainties, it is unlikely to significantly affect the conclusions presented here. 

\section{Future work}
Several future avenues arise from this thesis. The most significant is imaging and obtaining a total minihalo flux density for the remaining clusters in this sample. Expanding the analysed sample would strengthen the basis for the apparent absence of high-frequency spectral steepening in most minihalos. As discussed, achieving this primarily requires improvements in the self-calibration and source-subtraction procedures. 

A major methodological improvement would be the adoption of a physically motivated \textit{uv}-cut scaled to the expected angular extent of each minihalo. This would better isolate compact emission when constructing the subtraction model and reduce any redshift-dependent systematic bias. However, a simple \textit{uv}-cut may not be sufficient for ACTJ0022-0036, where the apparent minihalo extent is small due to its high redshift. For this cluster, direct modelling of the diffuse emission using the surface brightness, as performed by \citet{Knowles2019}, may be appropriate to provide a more robust approach. 

A more rigorous treatment of systematic effects would involve explicit modelling of the SZ signal for each cluster using gas pressure profiles, followed by propagation through the interferometer response, as demonstrated by \citet{Perrott2021}. This would enable direct correction for any SZ-induced bias in the measured minihalo flux densities, which is particularly important for fainter minihalos.

This thesis has focused primarily on the integrated spectral properties of the minihalo emission, with limited exploration of the spatially resolved structure. However, spatial morphology provides an additional diagnostic to analyse CRe production mechanisms. A point-to-point spectral comparison with previous low-frequency observations would test whether hadronic production and turbulent acceleration are operating over distinct spatial regions within individual minihalos. The smaller apparent extents observed at 10 GHz suggest that regions of spectral steepening, such as the tail of RXJ1720+2638, may be identified through spectral index mapping. 

The signal-to-noise ratio of the diffuse emission ultimately limits the steepest spectral index that can be robustly measured. One potential method for enhancing low surface-brightness emission is spatial smoothing, typically through convolution with a Gaussian kernel. While such averaging increases sensitivity to diffuse emission, it reduces angular resolution. As this can complicate source-subtraction, it would be best investigated on the source-subtracted images. This approach was not explored in this thesis and remains a potential avenue for improving the detectability of extended emission in future analysis of the 10 GHz observations.
