\chapter[Results]{Results}
\label{Chap:Results}

\section{RXJ1720+2638}
RXJ1720+2638 (also known as RXJ1720.1+2638) is a cool core galaxy cluster at $z = 0.160$ \citep{Owers2011}. Early observations detected the presence of two cold fronts, an edge to the south east and a plateau to the northwest \citep{Mazzotta2001}. This suggested the presence of a core dense cold gas cloud ($T \approx 4$ keV) embedded in the outer diffuse and hot ICM ($T\approx10$ keV), with the cold fronts likely arising via a minor merger. Weak gravitational lensing studies \citep{Okabe2010} and galaxy density mapping \citep{Owers2011} revealed the presence of a substructure $\sim550$ kpc north of the cluster core. \citet{Owers2011} suggest that a northward passage of this structure passing the core to the east, providing the perturbations to the core and inducing large scale gas sloshing. 

RXJ1720+2638 was one of the first two clusters where cold fronts and minihalos were found to have a correlation \citep{Mazotta2008}, resulting in a more detailed spectral analysis with \citet{Giacintucci2014a} analysing observations at six frequencies in the range 317 MHz to 8.4 GHz taken by the GMRT and VLA. This revealed three primary sources of minihalo emission in the core region, the central radio galaxy (BCG), a head-tail radio galaxy to the north east with a southward tail, and the minihalo emission. 

\begin{itemize}
    \item Sections for each minihalo with a brief explanation of imaging process, custom things we had to do to get results.
    \item Number of self calibration, sources subtracted, difficulties in imaging certain aspects.
    \item Discussion on the calibration error and variance in the observed point sources.
    \item Includes an image of the uvrange data showing point sources, image of the minihalo with contours, and anything else we desire.
    \item Includes discussion compared to previous results or measured values (likely G14) and any caveats or concerns.
\end{itemize}

