% ***************************************************
% PRELIMINARY PAGES
% ***************************************************
% The instructions contained within this part of the thesis template need to be suppressed from the final thesis. There are instructions on how to do this in the MainThesis.tex file.

% To ensure your work is not suppressed with the instructions please add your text only where instructed.

%***Acknowledgements***
\clearpage
\section*{Acknowledgments}
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}

\begin{instructional}
    \noindent
    Thank you first and foremost to my supervisor, Yvette Perrott, for your continued guidance and encouragement throughout this thesis. Without your never-ending patience and incredible ability to clarify the many questions and challenges I have faced, this thesis would not have possible.

    Thank you to my family and friends for supporting me throughout my Masters and allowing me to talk about my research while understanding nothing.

    Thank you to the administrative staff for the Raapoi High Performance Cluster at Victoria University of Wellington for their support. Thank you to the NRAO Science Helpdesk for answering several of my questions regarding \textit{CASA}.

    Artificial intelligence tools, ChatGPT (OpenAI, versions 4o, 5.1, and 5.2), were utilised in a supportive capacity over the course of this thesis. Assistance was provided in generation of code templates, plot styling, background research and concept clarification, and proofreading for understanding and flow.
    These tools were not used for any analysis of data, formation of conclusions, or writing sections of the thesis. All scientific results, conclusions, and final edits are the author's own work. 
\end{instructional}


% ***************************************************

%***Table of Contents***
%These generate the table of contents, list of figures, and list of tables from items tagged with a \label{} command.
\clearpage
\tableofcontents
\newpage

%***End of front matter***