\chapter[Introduction]{Introduction}
\label{Chap:Intro}

% ***************************************************
% Introduction
% ***************************************************

When looking up into the sky on a clear night, those without an interest in astrophysics might imagine many of the points in the sky as galaxies just like our own, floating alone in the deep void of space. Although true to an extent, it doesn't paint an accurate picture of the cosmos. In reality, many of these form galaxy clusters, with tens to thousands of individual galaxies becoming gravitationally bound into a single massive structure (somewhat analagous to the planets in our solar system, but on a vastly different scale).\footnote{Smaller clusters with only tens of galaxies are often known as groups.} Galaxy clusters are the largest gravitationally bound structures in the universe, with total masses of order $10^{14}$$-$$10^{15}$ \Msun{} and diameters larger than 1.5 million parsec.\footnote{For those unaccustomed to astrophysical units, \Msun{} is the solar mass and defined as 1 \Msun{} $\approx 10^{30}$ kg. A parsec is defined as 1 pc $\approx3\times10^{16}$ m. These unusual units are far more suitable at the scale of the universe.}

One might naturally expect that the majority of the cluster mass to be from the innumerable galaxies held within, however, only a few percent of the total mass comes from this baryonic matter (such as stars, planets, etc). The remainder of the baryonic mass comes from a hot diffuse gas ($10^7$$-$$10^8$ K) spread throughout the cluster called the intracluster medium (ICM). This dilute gas ($\sim10^3$ particles m$^{-3}$) is held together by the gravitational pull of the cluster, with the highest density in the core and sparsest at the edges \citep{Meekins1971, Serlemitsos1977}. Even then, this amount of visible baryonic matter only comprises 15\% of the gravitational mass calculated from the dynamics of the cluster, a huge discrepancy that was a key piece of evidence for the existence of dark matter. Indeed, the rough consensus from decades of study on galaxy clusters has $\sim3\%$ of the mass budget taken by galaxies, $\sim12\%$ from the ICM, and a staggering $\sim85\%$ from unobservable dark matter \citep{Blumenthal1984,Vikhlinin2006,Pratt2019}. 

Between these clusters, long filaments of galaxies span across space, with their own warm-hot intergalactic medium (WHIM) mimicking the role of the ICM. The WHIM is cooler and more diffuse than the ICM, with densities $\leq 10^2$ particles m$^{-3}$ and temperatures $10^5$$-$$10^7$ K. These filaments are larger than clusters, though not gravitationally bound, and create a cosmic web in the sky with galaxy clusters located at the intersections. This cosmic web is the largest structure in the universe, a vast network of dark matter that we can trace via the observable galaxies and clusters \citep{Bond1996,Pimbblet2005} with ongoing work in detecting these filaments observationally \citep{Tudorache2025}. Clusters are known to form in part due to accretion of the WHIM these at intersections of the cosmic web, as well as by mergers between smaller clusters \citep{Press1974, Voit2005, Kravtsov2012}. 

An important distinction should be made when analysing clusters, between ``disturbed'' clusters undergoing merger events or still in a turbulent state from a recent merger, and ``relaxed'' clusters which have settled into an undisturbed state. Relaxed clusters favour theoretical studies due to their greater spherical symmetries, fewer substructures, and therefore, simpler modelling \citep{Mantz2016}. Many relaxed clusters have also been found to feature a ``cool core'', where the temperature at the centre of the cluster is significantly lower than the region outside the core. The high density of the ICM in the core causes a large outflux of X-ray emission, great enough to lower the cooling time below the expansion rate of the universe (known as Hubble time)\stickynote{This can be stated better I think.}. In a closed system, this develops into a cooling flow causing the core temperature to drop and an inward gas flow \citep{Peterson2006,Hudson2010}. Observational evidence supports this theory, however, the magnitude of observed cold gas is much lower than predicted, implying the existence of a heating mechanism to counteract the cooling flow. One such source are active galactic nuclei (AGN), supermassive black holes at the centre of some galaxies that are consuming massive amounts of matter, and producing radio synchrotron emission. This emission creates jets and lobes that have been observed interacting with the ICM, distributing energy in ``radio-mode'' feedback \citep{Fabian2012}. The exact method of this heating is still disputed and undergoing research.

Within the high mass subset of relaxed cool core clusters ($M_{500}>6\times10^{14}$ \Msun)\footnote{The value $M_{500}$ refers to the total mass within a radius of $R_{500}$, defined by the distance at which the clusters average enclosed density is 500 times the critical density of the universe at the cluster redshift. The critical density is a cosmological quantity that has varied over the lifetime of the universe.} recent works have shown that 80\% contain radio minihalos \citep{Giacintucci2017}. Less common in lower mass clusters, and unobserved within non-cool core clusters, minihalos are diffuse radio sources with currently unknown origins. This radio emission is localised within the cool core, with radii from 50 kpc to 0.2$R_{500}$.\footnote{The radius 0.2$R_{500}$ is a standard metric to separate the core and the outer ICM. Within this radius, the cooling, AGN feedback, and similar processes become significant to the behaviour of the ICM.} This emission cannot be directly formed by radio sources such as AGN, as there is no observed spatial or spectral connection at any resolution or frequencies studied thus far. Furthermore, the spatial extent of these halos is well beyond the expected extent for particles sourced from an AGN (e.g. \citealp{Bagchi2002,Giacintucci2014}). Understanding the origins and physics behind minihalos is an ongoing process, with viable production methods proposed, but a lack of conclusive observational evidence to differentiate between them.  This thesis will provide new observational data and a generalised process to provide further evidence to differentiate between the proposed processes.

\section{Observations of Galaxy Clusters}

The question that should first be asked is, how \textit{do} we know all of this information about galaxy clusters? How are we able to measure the temperature, density, pressures within these clusters without travelling the impossibly vast distances to get there? The answer to this question is simple, by observing the radiation emitted from these structures. Different processes within the cluster, and more specifically ICM, provide information about the physical environment. This radiation is emitted across the electromagnetic spectrum and we design telescopes to capture and relay different bands in order to identify different components of what we observe. The question then becomes, how do observations at different frequency bands inform us to the structure and processes occuring within a cluster? 

\subsection{Optical}

The vast majority of optical light from clusters comes from stars within the component galaxies. Although incredibly informing about the stars and galaxies themselves, in the context of minihalos, optical light has limited use. Optical observations are useful in determining the component galaxies of a cluster, alongside investigating the radial velocities of galaxies. Since the radial velocity is dependent on the gravitational potential of the cluster, the distribution allows us to estimate the clusters mass \citep{Voit2005}. This analysis is difficult for more distant clusters and disturbed clusters, as the dynamical state will affect the radial velocities and skew the resulting mass.

\subsection{X-ray}
The hot gas of the intracluster medium forms a thin plasma, which has a degree of ionisation that depends on the temperature and density. We observe an X-ray spectrum from this gas with both continuum and line characteristics, and photon energies between 0.1 keV and 100 keV.\footnote{X-ray emission is historically measured in kilo-electron volts (energy) rather than frequency or wavelength.} The energy of the photons is dependent on the temperature of the ICM, resulting in most emissions being in the narrower range of 1 to 10 keV \citep{Schneider2015}. 

Line emission occurs due to electron transitions between orbitals within an atom. The temperature and density of the ICM changes the measured rate of this line emission, however, this becomes limited at higher temperatures as the ionisation fraction increases. The distribution of line emissions can also be an indicator of abundance of elements such as C, N Ne, Mg, Si, S, Ar, Ca, and Fe. This is particularly evident at lower temperatures ($\lesssim 2$ keV) where the total emissions can be dominated by line emission \citep{Voit2005, Schneider2015}.

Continuum radiation is due to brehmsstrahlung, or free-free radiation, which is where electrons are deflected via Coulomb interaction with nearby nuclei. This deflection causes an acceleration induces a change in kinetic energy which is emitted as a photon. The spectral energy distribution of these emissions is related to the kinetic energy of the particles, and therefore, the temperature of the ICM. The scale of emissions is similarly impacted by the number of particles, and thereby the density of the ICM $\rho_g$ in a given region. This gives rise to the following relationship to total continuum emissivity \citep{Schneider2015}.
\begin{equation}
    \epsilon_{c} \propto T^\frac12 \rho_g^2
\end{equation}

X-ray spectroscopy is a powerful tool to characterise the ICM and a clusters dynamical state. In general, telescopes trade off between high spatial or spectral resolutions, i.e. between detecting exactly where a photon originated from or an accurate measurement of the photon energy. This becomes somewhat of a constraint when observing galaxy clusters as we require reasonable spatial and spectral resolutions for these large objects. One common instrument is the space telescope \textit{Chandra X-ray Observatory} launched in 1999\stickynote{Cite/footnote telescopes}. Many studies of minihalos use \textit{Chandra} observations to map the structure of the cool core and investigate potential relationships to the radio emission (e.g. \citealp{Giacintucci2024}). However, due to the aging detectors and contaminant build up on \textit{Chandra}, the sensitivity of the telescope is decreasing. This is particularly bad at low energies ($<2$ keV), where sensitivity is below $10$\% of where it was two decades ago \citep{Grant2024}. A new telescope \textit{XRISM} was launched in late 2023 and was designed as a successor to \textit{Chandra}. Over the last year researchers have begun to utilise the greater resolution to more deeply probe the dynamics of the ICM in some clusters \citep{Sarkar2025, XRISM2025}. Although not the focus of this thesis, X-ray observations provide key ancillary data in investigating the processes involved.

\subsection{Radio}

Radio observations cover several orders of magnitude, with frequencies from 10 MHz to over 100 GHz. This massive range comes with several difficulties for astronomers, with the primary one being the angular resolution of the telescope. Angular resolution $\theta$ defines the smallest area that can be resolved given an aperture and the observing wavelength.\footnote{The angular resolution of a human eye (with 20/20 vision) is 1 arcminute. \textit{See note 7}} Equation \ref{eq:angular_resolution} gives the formula for angular resolution in arcseconds, or $\frac1{3600}$th of a degree, for an aperture of diameter $D$ and observing wavelength $\lambda$.\footnote{Arcseconds ($"$), arcminutes ($1' = 60"$), and degrees are common units in astrophysics as declination, the celestial equivalent to latitude, is measured in these units.} 
\begin{equation}
    \theta = 2.5\times10^5\frac\lambda D
    \label{eq:angular_resolution}
\end{equation}
Radio waves range from 3 cm to 3 km, orders of magnitude larger than optical ($\sim1\mu$m) and X-ray ($0.01$$-$$10$ nm). It is then clear that to resolve the same object at radio frequencies as X-ray or optical, vastly larger telescopes would be necessary. In order to observe over this range several types of telescopes have been developed, including single dish telescopes, interferometer arrays, and very long baseline interferometry (VLBI). 

The size of a single dish antenna is limited by both practical construction and from scientific usability. The largest dish is the \textit{Five-hundred-meter Aperture Spherical Telescope} (FAST) located in Guizhou China, though of the 500 metre diameter only a 300 metre area is usable at a time. Furthermore, as an immovable dish, it is limited in its view of the sky, with a maximum angle of 40 degrees from zenith. Several smaller 100 metre diameter dishes exist such as the \textit{Green Bank Telescope} in West Virginia United States, and the \textit{Effelsburg Telescope} near Bonn, Germany.\stickynote{Cite/footnote telescopes} These dishes also have a limited view of the sky and variable amounts of steerability due to their size, alongside hard limits on their resolution at higher radio frequencies. These restrictions developed into interferometry, the use of an array of single dish telescopes in tandem to simulate a larger dish. The \textit{Karl G. Jansky Very Large Array} (VLA) in New Mexico United States, is comprised of 28 fully steerable 25-metre radio telescopes mounted on railway tracks in a Y-shaped array, observing between 73 MHz and 50 GHz. The \textit{MeerKAT} telescope in the Meerkat National Park of South Australia contains 64 13.5-metre telescopes and operates between 1000 MHz and 10 GHz. These arrays can simulate observations by dishes several kilometres in diameter, while being able to observe to low sky elevations. VLBI takes this concept even further by using radio telescopes across different continents, synchronised by atomic clocks, to simulate dishes comparable to the size of the Earth. This thesis uses observations taken by the VLA, and the physics of these telescopes will be discussed in more detail in Chapter \ref{Chap:Background}. 

Radio emission detected by these telescopes falls into the category of `synchrotron' emission. This synchrotron emission is produced by particles travelling at relativistic velocities through a magnetic field, emitting photons at radio energies characterised by their velocity and the magnetic field strength \citep{Ferreti2012,Schneider2015}. This is due to the Lorentz force ($\vec F = \vec v \times \vec B$) perpendicular to their direction of motion, which induces a helical path through the field, and therefore constant acceleration. This is analagous to brehmsstrahlung radiation, but occurs due to a magnetic interaction instead electric, which is why it is somewhat rarely called `magnetobrehmsstralung'. A detailed discussion of the spectral distribution and features of this radiation is given in Chapter \ref{Chap:Background}.

\subsection{Gamma}

The last region of interest for minihalo research is in detecting gamma radiation, or gamma-rays. This is the high energy limit for astronomy, where telescopes are designed to detect photons with energies in the MeV and GeV range.\footnote{Like X-ray, gamma-rays are measured by their energy rather than frequency.} These prove difficult to not only detect, due to the majority of rays being absorbed in the atmosphere, but also to accurately describe their origin \citep{Schneider2015}. The \textit{Fermi Gamma-ray Space Telescope} was built specifically for this research and was launched in 2008 carrying the Large Area Telescope (LAT), with an energy range between 30 MeV and 300 GeV. 

There are various sources for gamma-rays, such as Gamma Ray Bursts (GRB), which are extremely short and intense flashes. Many of these have been spatially located to coincide with bright AGNS called blazars, and rapidly spinning magnetised neutron stars called pulsars. Another source is from gamma-ray background radiation, which is expected be via neutral pion decays resulting from proton-proton collisions. Attempts to detect gamma-ray emissions connected to a clusters ICM have been ongoing as they allow us to put limits on effectiveness of proposed mechanisms to create radio halos (e.g. \citealp{Reimer2003,Ackermann2010,ZandanelGamma2014}). Though progress has been made for giant radio halos, in particular firm constraints for the Coma cluster \citep{Brunetti2012}, minihalos have a smaller spatial extent and are much fainter, with no conclusive studies. The role of gamma rays in determining the processes creating minihalos is detailed in Chapter \ref{Chap:Background}.

\section{Diffuse Radio Emission}
\stickynote{Add a picture for a minihalo. Maybe Perseus from Fig 3 \citet{vanWeeren2019} or own.}
It has long been known that some clusters exhibit diffuse radio synchrotron emission that cannot be directly associated with radio galaxies within the cluster. This synchrotron emission can take many spatial arrangements, with the primary categories being radio halos, radio relics, and revived AGN sources. Radio halos are extended sources that trace the ICM distribution and operate at the scales of giant radio halos, matching the full ICM extent, and minihalos that are contained within a clusters cool core. Relics instead reflect particles that have been reaccelerated to relativistic energies by shock waves travelling through the ICM, such as the violent energies released during merger events. Revived AGN sources are radio plasma that has been emitted from and AGN and re-energised similarly to the radio relics. 

\subsection{Production}
A key question in relation to the radio halos is how they are produced. The relativistic particles producing this emission have a characteristic lifetime due to the energy losses as they travel through space, and therefore a limited diffusion length-scale in which we should be able to observe them. Within a weak magnetic field ($\sim10^{-7}$ G) these distances are about 10 pc, which even accounting for bulk motion of the ICM and more favourable diffusion environments are well below the Mpc scales observed in many clusters \citep{Bagchi2002}. Two primary theories have been brought forward to explain this phenomenon, one being turbulence in the ICM causing ``reacceleration'' of once relativistic particles (e.g. \citealp{Brunetti2001,Gitti2002,ZuHone2013,Zandanel2014}). The other is inelastic collisions between relativistic cosmic ray protons and thermal protons, termed ``hadronic'' or secondary production (e.g. \citealp{Dennison1980,Dolag2000,Keshet2010,ZuHone2015,Ignesti2020}). 

Both of these mechanisms produce similar observable features, which makes disentangling the true source much more challenging. Investigation into spatial extents and spectral features of giant radio halos has given the reacceleration theory more credence than hadronic production \citep{Brunetti2012}, however, the debate is still ongoing for minihalos. A detailed explanation of these processes is provided in Section \ref{sec:BG_reacceleration} and \ref{sec:BG_hadronic}. Due to their faint nature and smaller size, observations require high sensitivity and resolution in order to accurately capture an image. 

\subsection{Minihalo detections}
Much effort has been devoted towards detection and validation of minihalos in order to build a comprehensive sample. Over the last two decades the number of detected minihalos has increased substantially, from 10 minihalos and minihalo candidates in 2011 \citep{Ferreti2012}, to 22 in 2017 \citep{Giacintucci2014}, and 40 in 2024 \citep{Giacintucci2024}. A recent sample of 23 confirmed minihalos is detailed by \citet{Giacintucci2019}, though several more have been confirmed since (e.g. \citealp{Richard-Laferri2020, Kale2022, Lusetti2024}). 

One of the major issues with detection is in separating the minihalo emission from the much brighter sources embedded within and nearby it. Alongside the minihalo in the core is the brightest cluster galaxy (BCG), the most radio-loud AGN within the cluster. Minihalos typically have a surface brightness of $1\sim5$ $\mu$Jy arcsec$^{-2}$, while the BCG can have a flux 1000 times higher.\footnote{The Jansky (Jy) is a unit measurement of spectral flux density common in radio astronomy. It measures the rate of energy received per square meter per hertz, or $10^{-26}$W m$^{-2}$ Hz$^{-1}$ in SI units.} The BCG must then be masked or subtracted away from an observation to reveal the minihalo, but this requires the observation to have good resolution of point sources as well as the larger spatial minihalos. This requirement makes current general sky surveys insufficient for detecting minihalos, with some studies suggesting that next generation radio telescopes could reveal thousands more minihalos due to improved capabilities \citep{Gitti2018}.

\section{This Thesis}
\subsection{Aims}
The primary goal of this thesis is to calibrate, image, and analyse new radio observations of 12 minihalos at 10 GHz. These observations were performed by the VLA in C and D configuration over two periods in early 2024 and early 2025. This data constitutes the first broad survey of minihalos at high radio frequencies. 

This data will complement previous surveys at lower frequencies taken by the \textit{Low-Frequency Array} (LOFAR) at 140 MHz and MeerKAT at 1.3 GHz \citep{Riseley2022}. Processing this data will allow measurements of the minihalo flux to investigate if steepening of the spectrum occurs at higher frequency, which will assist in differentiating between the reacceleration and hadronic scenarios. 

\subsection{Work}
In pursuing these aims, I downloaded the raw interferometric data from the National Radio Astronomy Observatory (NRAO) Archive\footnote{\url{https://data.nrao.edu/portal/}} and documented the calibration and imaging process. I then performed various analyses on the final images for each minihalo to evaluate the limits and usefulness of 10 GHz observations for characterising the production mechanisms of minihalos.

This work was done in a source controlled repository\footnote{\url{https://github.com/MoonlitMoo/Masters-2025}} so that the results are reproducible and documented. Due to the size of the datasets, (uncalibrated $\sim1.4$ TB compressed, calibrated $\sim2.5$ TB, imaging $\sim?$\stickynote{Add final size} TB), this is stored on the Storage fOr Learning And Research (SOLAR) large scale storage provided by Victoria University of Wellington. 

The repository is split into two primary sections, \textit{Data Processing} and \textit{Image Processing}. The first section follows the calibration of the raw data and separation from observation runs into cluster specific datasets, split by observation id. The following image processing includes the cleaning and creation of the images from the trimmed datasets and the associated analysis and is split by cluster.

\subsection{Layout}
The introduction gives a brief overview for important concepts relating to minihalo physics and research. 

Chapter \ref{Chap:Background} details previous research on minihalos and deeper explanation of the hadronic and turbulent reacceleration processes.

Chapter \ref{Chap:Calibration} introduces the collected data and explains the calibration and imaging process used.

Chapter \ref{Chap:Analysis} explains the tools and techniques used in the analysis of the final images.

Chapter \ref{Chap:Results} details the results found for each cluster, with the context of previous studies.

Chapter \ref{Chap:Discussion}

Chapter \ref{Chap:Conclusion}

